\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainty (Not Finished Work)

### 2014-07-07 paper.tex
removd abstract

\title{\LARGE \bf
Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity }

@@

\vspace{10pt}
\noindent{\textbf{Grasp Quality Metrics}}: A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
We use the wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces.
We also consider the general case where there is friction at the contact points.\\

\noindent{\textbf{Gaussian Process (GP) Primer}}: Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006}.
In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}, ~\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$.
The observations are assumed to be noisy measurements from the unknown target function $f$:
\begin{equation}
y_i = f(\bx_i) + \epsilon,
\end{equation}
where $\epsilon \sim \mN(0,\sigma^2)$ is Gaussian noise in the observations.
A zero-mean Gaussian process is completely specified by a covariance function $k(\cdot,\cdot)$, also referred to as a kernel.
Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2006}:
\begin{equation}
  p(f_*|\bx_*,\mD) 
  \sim 
  \mN\big(k(\mX,\bx_*)^{\intercal}(K + \sigma_{\epsilon}^2I)^{-1}\by,
\end{equation}
\[
  k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big), \label{eq:GPposterior}
\]
where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$.

>>>>

\title{\LARGE \bf
Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainty (Not Finished Work) }

@@

\vspace{10pt}
\subsection{Grasp Quality Metrics}
 A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
We use the wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces.
We also consider the general case where there is friction at the contact points.\\

\subsection{Gaussian Process (GP) Primer}
 Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2006}.
In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}, ~\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$.
The observations are assumed to be noisy measurements from the unknown target function $f$:
\begin{equation}
y_i = f(\bx_i) + \epsilon,
\end{equation}
where $\epsilon \sim \mN(0,\sigma^2)$ is Gaussian noise in the observations.
A zero-mean Gaussian process is completely specified by a covariance function $k(\cdot,\cdot)$, also referred to as a kernel.
Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2006}:
\begin{equation}
  p(f_*|\bx_*,\mD) 
  \sim 
  \mN\big(k(\mX,\bx_*)^{\intercal}(K + \sigma_{\epsilon}^2I)^{-1}\by,
\end{equation}
\[
  k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big), \label{eq:GPposterior}
\]
where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$.
